Title on one or two lines without capitals, except after a colon

### 2020-06-23 Report/CJS_Sample.tex
Preliminary Simulation Study Results DONE

% Single-author journal article
\bibitem[]{bib2}
Cleveland, W. (1979). Robust locally-weighted regression and smoothing scatterplots. 
{\it Journal of the American Statistical Association}, 74, 829-836.

@@

% Edited book
\bibitem[]{bib8}
Roberts, G., Ren, Q., \& Rao, J.~N.~K. (2009). 
Using marginal mean models for data from longitudinal surveys
with a complex design: Some advances in methods. In Lynn, R. (Ed.) {\it Methodology of Longitudinal Surveys}, 
John Wiley \& Sons, New York, 351-366.
\end{thebibliography}

>>>>

% Single-author journal article
\bibitem[]{bib2}
Cleveland, W. (1979). Robust locally-weighted regression and smoothing scatterplots. 
{\it Journal of the American Statistical Association}, 74, 829-836.

@@

% Edited book
\bibitem[]{bib8}
Roberts, G., Ren, Q., \& Rao, J.~N.~K. (2009). 
Using marginal mean models for data from longitudinal surveys
with a complex design: Some advances in methods. In Lynn, R. (Ed.) {\it Methodology of Longitudinal Surveys}, 
John Wiley \& Sons, New York, 351-366.
\end{thebibliography}
